---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(tidyr)
library(tidyverse)
library(ggplot2)
```
```{r}
Ma_percapita<-read.csv("Per_capita_personal_income.csv")
```

## Including Plots

You can also embed plots, for example:

```{ r percapita echo=FALSE}
ggplot(data = Ma_percapita, mapping = aes(x = name, y=per_capita_2020,fill=name)) +
  geom_col()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(title= "Percapita of MA cities in the year 2020",x="county",y="percapita",fill="County names")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
